Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-12 paper/galsize_paper.tex
Minor changes to grammar in conclusions. Added link to GitHub repo.

Our results can be treated as a starting point for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations. For convenience, Figure \ref{fig:censatsizeratios} provides a simple summary statistic that can be used as a diagnostic for calibrating alternative modeling efforts. We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.

Our publicly available python code provides a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web. Mock catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf$ will be made publicly available upon journal publication; prior to that time, our mocks are available upon request.

@@

This research was supported in part by the National Science Foundation under Grant No. NSF PHY11-25915. Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357. AK was  supported by NSF grant  AST-1412107 and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897 and an endowment from the Kavli Foundation and its founder Fred Kavli.

>>>>

Our results provide an integral constraint for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations. For convenience, Figure \ref{fig:censatsizeratios} provides a simple summary statistic that can be used as a diagnostic for calibrating alternative modeling efforts. We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.

Our python code is publicly available on GitHub;\footnote{\url{https://github.com/aphearin/galsize_models}} we intend for this to provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web. Tabulations of our clustering measurements, as well as catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf,$ will be made publicly available upon publication; prior to that time, our measurements and mock data are available upon request.

@@

Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357. This research was supported in part by the National Science Foundation under Grant No. NSF PHY11-25915.  AK was  supported by NSF grant  AST-1412107, and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897, and an endowment from the Kavli Foundation and its founder Fred Kavli.
